Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-02 manuscript.tex
Error X ratio figure
Included gzz with height plot and better captions

\begin{figure}
    %\centering
    %\includegraphics[width=0.4\textwidth]{figs/distance-size-curves}
    \missingfigure{}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models:
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        2 km height at the polar region,
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        2 km height at the equatorial region,
        $1^\circ \times 1^\circ$ tesseroids with computation grid at
        260 km height at the polar region,
        and
        $30^\circ \times 30^\circ$ tesseroids with computation grid at
        2 km height at the polar region.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    %\centering
    %\includegraphics[width=0.4\textwidth]{figs/gzz-with-height}
    \missingfigure{}
    \caption{
        Variation of $g_{zz}$ difference curves for computation grids at
        varying heights.
    }
    \label{fig:gzz-with-height}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/distance-size-curves}
    %\missingfigure{}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/gzz-with-height}
    %\missingfigure{}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
    }
    \label{fig:gzz-with-height}
\end{figure}
